Go Implementation of Up-To Techniques for Equivalence of Weighted Languages

### 2020-10-02 paper/notused.tex
working on experimental data

>>>>

\begin{defn}
  \textbf{Algorithm for computing the null space of a vector subspace} \\
  The algorithm implementation can be found in file \texttt{lin/nullspace.go}; it is
  adapted from \cite{scipy/ranknullspace}. 
  Let's consider the singular value decomposition of a matrix $A \in \R^{m \times n}$:

  \begin{equation*}
    \begin{aligned}
      A = U \Sigma V^T & \quad & \Sigma = \diag{\sigma_1, \sigma_2, \hdots, \sigma_{\min(m, n)}  } 
       & \quad &  U \in \R^{m \times m} & \quad & V \in \R^{n \times n}
    \end{aligned}
  \end{equation*}

  Where $V$ and $U$ are orthogonal and the singular values are ordered: $\sigma_1 \geq \sigma_2 \geq \hdots \geq \sigma_{\min(m,n)} \geq 0$.
  It follows that $\mrank{A}$ is equal to the number of nonzero singular values and
  a basis of the (right) null space of $A$ is the spanning set of the columns of V
  corresponding to singular values equal to zero. 
\end{defn}

\begin{exmp}
  First, we show a shorter Python 
  implementation of the algorithm to compute the nullspace, using the 
  \textit{SciPy} library \cite{scipy/ranknullspace}:

  \lstinputlisting[language=python]{nullspace.py}

    The Go implementation is quite longer:

    \lstinputlisting[language=go]{../lin/nullspace.go}

\end{exmp}

### 2020-10-02 paper/paper.tex
working on experimental data

\begin{proof}
  Proved in section 3.2 of \cite{BONCHI201277}
\end{proof}

@@

\section{The Problem}
In this work, we

@@

The algorithm is defined by the iterative method:
\begin{eqnarray}
  R_0 = \mker{o}^0, & \quad & R_{i+1} = R_i + \sum_{a \in A} t_a^t(R_i) \label{back} 
\end{eqnarray}
Where $\mker{o}^0$ is an annihilator.
The algorithm stops when $R_{j+1} = R_j$. Proof is available in section 4.2 of \cite{BONCHI201277}

@@

See Section \ref{sec:headings}.

\begin{defn}
  \textbf{Algorithm for computing the null space of a vector subspace} \\
  The algorithm implementation can be found in file \texttt{lin/nullspace.go}; it is
  adapted from \cite{scipy/ranknullspace}. 
  Let's consider the singular value decomposition of a matrix $A \in \R^{m \times n}$:

  \begin{equation*}
    \begin{aligned}
      A = U \Sigma V^T & \quad & \Sigma = \diag{\sigma_1, \sigma_2, \hdots, \sigma_{\min(m, n)}  } 
       & \quad &  U \in \R^{m \times m} & \quad & V \in \R^{n \times n}
    \end{aligned}
  \end{equation*}

  Where $V$ and $U$ are orthogonal and the singular values are ordered: $\sigma_1 \geq \sigma_2 \geq \hdots \geq \sigma_{\min(m,n)} \geq 0$.
  It follows that $\mrank{A}$ is equal to the number of nonzero singular values and
  a basis of the (right) null space of $A$ is the spanning set of the columns of V
  corresponding to singular values equal to zero. 
\end{defn}

\begin{exmp}
  First, we show a shorter Python 
  implementation of the algorithm to compute the nullspace, using the 
  \textit{SciPy} library \cite{scipy/ranknullspace}:

  \lstinputlisting[language=python]{nullspace.py}

    The Go implementation is quite longer:

    \lstinputlisting[language=go]{../lin/nullspace.go}

\end{exmp}

\subsection{Implementing the backwards algorithm}

In \cite{BONCHI201277}, for the first step of the iterative backwards 
algorithm to compute the largest linear weighted bisimulation, we 
need to compute $\mker{o}^0$. If $V$ is a vector space and $W$ is a
subspace of $W$, the annihilator of $W$, respectively $W^0$ is 
a subspace of the space $V^*$ of linear functionals on $V$.
$W^0$ are the functionals that annihilate on $W$. Since 
we are working on subspaces of $\R^n$, we can directly compute 
the orthogonal complement in our implementation instead of the
annihilator.

@@

\subsubsection{Headings: third level}

\paragraph{Paragraph}

\section{Examples of citations, figures, tables, references}
\label{sec:others}

\cite{kour2014real,kour2014fast} and see \cite{hadash2018estimate}.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations
appropriate for use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}

\subsection{Figures}
See Figure \ref{fig:fig1}. Here is how you add footnotes. \footnote{Sample of the first footnote.}

@@

\subsection{Tables}
See awesome Table~\ref{tab:table}.

>>>>

\begin{proof}
  Proved in section 3.3 of \cite{BONCHI201277}
\end{proof}

Language equivalence can be expressed in terms of linear weighted bisimulations (LWBs for short).
Differently from weighted bisimulations, LWBs can be seen both as relations and as subspaces.
The subspace representation of LWBs is used in the backwards partition refinement algorithm 
implemented in \cite{BONCHI201277} and in this work.

@@

\section{The Problem}
We want to check if two vectors are language equivalent $v_1 \sim_l v_2$.

@@

The algorithm is defined by the iterative method:
\begin{eqnarray}
  R_0 = \mker{o}^0, & \quad & R_{i+1} = R_i + \sum_{a \in A} t_a^t(R_i) \label{back} 
\end{eqnarray}
Where $\mker{o}^0$ is an annihilator.
The algorithm stops when $R_{j+1} = R_j$. An index $j \leq \dim(V)$ is 
guaranteed to exist, such that the algorithms terminates at step $j$.
It follows that $\llwb \equiv R_j^0$.
Proof is available in section 4.2 of \cite{BONCHI201277}

@@

\begin{defn}
  \textbf{Applications of SVD} \\

  Let's consider the singular value decomposition of a matrix $A \in \R^{m \times n}$:

  \begin{equation*}
    \begin{aligned}
      A = U \Sigma V^T & \quad & \Sigma = \diag{\sigma_1, \sigma_2, \hdots, \sigma_r  } 
       & \quad &  U \in \R^{m \times m} & \quad & V \in \R^{n \times n}
    \end{aligned}
  \end{equation*}

  Where $V$ and $U$ are orthogonal and the singular values are ordered: $\sigma_1 \geq \sigma_2 \geq \hdots \geq \sigma_r \geq 0$.
  It follows that $\mrank{A}$ is equal to the number of nonzero singular values, and
  as explained in \cite{svd}:

  \begin{enumerate}
    \item  $\mrank{A} = \mrank{\Sigma} = r$
    \item The column space of $A$ is spanned by the first $r$ columns of $U$.
    \item The null space of $A$ is spanned by the last $n − r$ columns of $V$.
    \item The row space of $A$ is spanned by the first $r$ columns of $V$.
    \item The null space of $A^T$ is spanned by the last $m − r$ columns of $U$.
  \end{enumerate}

  Of our interest, are only the computation of the null space and columns space.
  The implementation, applying SVD, 
  can be found in files \texttt{lin/colspace.go} and \texttt{lin/nullspace.go}.
\end{defn}

\subsection{Implementing the backwards partition refinement algorithm}

To compute $\llwb$ at the last step of the algorithm,
we need to compute $R_j^0$.
If $V$ is a vector space and $W$ is a
subspace of $W$, the annihilator of $W$, respectively $W^0$ is 
a subspace of the space $V^*$ of linear functionals on $V$.
$W^0$ are the functionals that annihilate on $W$. Since 
we are working on subspaces of $\R^n$, we can directly compute 
the orthogonal complement in our implementation instead of the
annihilator.

@@

%=============================================================

@@
